Stellar and Planetary Properties of \KT\ Campaign 1 Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-18 ms.tex
ao section

One system, EPIC 201828749, is known to be a binary through AO imaging
as discussed in \ref{sec:AO}. \btmtodo{More text...}

@@

This is Brendan.

Images for all systems AO data was obtained for is shown in Fig. \ref{Fig:AO}.

\begin{figure*}[htbp]
\centerline{\includegraphics[width=1.0\textwidth]{f2}}
\caption{AO data for all systems imaged.
The main frame for each single system shows the deep, saturated image.
The inset for each single system shows a shallower, unsaturated image to better
identify companions at close projected orbital separations.
For the two systems with imaged companions, EPIC 201546283 and 201828749,
only unsaturated frames are collected.
All subplots, including insets, are plotted on the same scale.}
\label{Fig:AO}
\end{figure*}

@@

\subsection{Known Background Stars}
The PHARO AO system has a field of view of NUMBER arcseconds.
\btmtodo{Check with Brendan to find this number}.
Each \KT\ pixel is a square of $3.98 \times 3.98$ arcseconds.
A background eclipsing binary within a few \KT\ pixels of our target
stars could mimic a transit signal inside our aperture while evading detection
by PHARO.
Such wide eclipsing binaries should appear in seeing-limited ground-based
surveys.

@@

\begin{figure*}[htbp]
\centerline{\includegraphics[width=1.0\textwidth, trim=0 6.30cm 0 6.30cm, clip=true]{f3}}
\caption{Imaging for EPIC 201912552 from 1955 to 2002. There is no background
object directly behind the present day location of the target (red circle) that could be missed
by the AO observations, while modern SDSS imaging can rule out wide companions
that may have been missed at wide separations, beyond the AO field of view.
All subplots are on the same scale.}
\label{fig:archival}
\end{figure*}

>>>>

One system, EPIC 201828749, is known to be a binary through AO imaging
as discussed in \textsection\ref{sec:AO}. 
In this case, we do account for the dilution induced by the companion. 
From our relative $JHK$ photometry of the two stars, we infer an expected flux
ratio between the two stars in the \kep\ bandpass, inflating the transit depth by 
this factor to account for the dilution. 
We marginalize  \dfmtodo{More text...}

@@

We obtained high resolution images of seven stars with the 
Palomar High Angular Resolution Observer (PHARO) infrared detector 
\citep{Hayward01} behind the PALM3000 adaptive optics system \citep{Dekany13}
at the Palomar 5.1-meter Hale telescope on the nights of 2015 Feb 3 and 4 UT.
Sky conditions were mostly clear with light cirrus and $\approx$1$\farcs$0--1$\farcs$3 seeing
on both nights.  
We used the smallest plate scale of 25~mas pix$^{-1}$ which resulted
in a field of view of 25$\farcs$6$\times$25$\farcs$6 across the 1024$^{2}$ pix$^{2}$ array.
All observations were obtained with the 32x pupil sampling mode, resulting in Strehl ratios
of $\approx$20--30\% in $K_S$ for our $V$=11--13~mag targets as measured by the Strehl
monitor at the telescope in real time.
We obtained unsaturated dithered frames of each target in $K_S$-band with typical 
integration times of 2--10~s.
Except for EPIC~201828749 and EPIC~201546283, which had nearby candidate 
binary companions, we also 
acquired deep saturated images (5--10 frames at 60 sec each) 
to search for fainter companions.

Images were registered and contrast curves were generated following \citet{Bowler15a}.
For the saturated data, the star's position in each image was found by masking the
saturated region and fitting a 2D bivariate Gaussian to the PSF wings.  
Contrast
curves for the median-combined image are calibrated using the unsaturated frames.  
The typical sensitivity is 6.5--7.5~mag at 1$''$.
The images were astrometrically calibrated using dithered observations of the 
Trapezium cluster centered
on $\theta$$^1$~Ori~C taken on 2015 Feb 3 UT.  
Based on the reference astrometry for pairs of stars in the field from
\citet{McCaughrean94}, we measure a plate scale of 25.2~$\pm$~0.4~mas pix$^{-1}$ 
and north orientation of --0.2~$\pm$~0.3$^{\circ}$.  
Since this latter value is consistent with being aligned with 
the detector columns, we adopt a value of 0.0~$\pm$~0.3$^{\circ}$ for this work.
Relative photometry of nearby stars is carried out using aperture photometry with 
an aperture radius of 12~pix (0$\farcs$3).  
For EPIC~201828749, we also acquired $J$- and $H$-band images.
Astrometry and photometry is derived separately for each image, and the mean and standard deviation 
of these measurements is adopted for our final values listed in Table~XX.

Images for all systems AO data was obtained for is shown in Fig. \ref{Fig:AO},
while contrast curves showing the $5\sigma$ limits for detection
as a function of orbital separation are given in Fig. \ref{Fig:CC}.

\begin{figure*}[htbp]
\centerline{\includegraphics[width=1.0\textwidth]{f2}}
\caption{AO data for all systems imaged.
The main frame for each single system shows the deep, saturated image.
The inset for each single system shows a shallower, unsaturated image to better
identify companions at close projected orbital separations.
For the two systems with imaged companions, EPIC 201546283 and 201828749,
only unsaturated frames are collected.
The pixel scale is 0.0252$\arcsec$ per pixel, and each subplot is a square 400 pixels
on a side. 
Each inset is a square 100 pixels on a side.
All subplots, including insets, are plotted on the same scale.}
\label{Fig:AO}
\end{figure*}

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.5\textwidth]{f3}}
\caption{$5\sigma$ contrast curves for all systems with AO nondetections.
For all systems, we can exclude the possibility that a companion at a given $\Delta K_S$
exists. 
From our known transit depths, we can then rule out significant parameter space in which 
an eclipsing binary could reside and mimic a transit signal.}
\label{Fig:CC}
\end{figure}

@@

\subsection{Known Background Stars}
The PHARO AO system has a field of view of 25 arcseconds.
Each \KT\ pixel is a square of $3.98 \times 3.98$ arcseconds.
A background eclipsing binary within a few \KT\ pixels of our target
stars could mimic a transit signal inside our aperture while evading detection
by PHARO.
Such wide eclipsing binaries should appear in seeing-limited ground-based
surveys.

@@

\begin{figure*}[htbp]
\centerline{\includegraphics[width=1.0\textwidth, trim=0 6.30cm 0 6.30cm, clip=true]{f4}}
\caption{Imaging for EPIC 201912552 from 1955 to 2002. There is no background
object directly behind the present day location of the target (red circle) that could be missed
by the AO observations, while modern SDSS imaging can rule out wide companions
that may have been missed at wide separations, beyond the AO field of view.
All subplots are on the same scale.}
\label{fig:archival}
\end{figure*}
